\font\myfont=cmbx12 at 20pt
\Large
{\myfont Acknowledgements}

I am very grateful to everyone at the Physics department for making my time at Royal Holloway as enjoyable as it has been. Firstly I would like to thank my supervisor Gregory Ashton for his patience, guidance and help over the past three years. From listening to my stupid questions as I navigated my way around first year tutorial questions and mentoring my way through this project he has had the patience of a saint to listen to my every request regardless of how elementary or obvious it is.

To all my friends at Royal Holloway, especially the eleven I lived with at Carfax, thank you all for making my time at university so enjoyable and being the wonderful people that you are. I would also like to acknowledge the people at the university's Motorsport Club, being your president for the last two years has been a dream come true. 

To my amazing friends from the Harvey Grammar School, Luca, Louis, Rakchit, Dan, Chester, Sam, and Bill, Freyja thank you. For the times we spend together, for the many games played together, and for the late night talks thank you all.

I must thank my family, my parents Jane and Andy, my sisters Millie and Josie for all the love and support through all these years thank you all for helping me through my education and life in general at every step.

To my darling partner Emily, I sincerely thank you, and I say it with more depth and heartfelt intention than I have ever had with these words before. With you by my side for the last ten years I have felt invincible at times and when I've been at my worst you were there to keep me going. You have been my source of motivation throughout this degree and I can't wait for our future together. I love you, always.

\newpage

\newgeometry{left=3cm, right=3cm, top=7cm, bottom=2cm}

\begin{center}
    \emph{This dissertation is dedicated \\ to the honour and memory of \\ Melodie Rose Pinckney.}
\end{center}

\restoregeometry